Modelling potential environmental impacts of science activity in Antarctica

### 2024-12-12 paper/paper.qmd
updated discussion/conclusion bullets

## Discussion {#sec-discussion}
To cover:
+ Figure of the largest study site?
+ Limitations of the method:
  + Data concerns, esp. opportunistic nature of the GPS data
  + Would higher resolution network be useful?
  + Reliance of shortest paths as a guide to behaviour
  + Some minor issues regarding the difference between directed and undirected graphs
+ Relevance of radius limits on betweenness: the implicit model of movement in this approach (short horizons, no existing paths, 'keep going for half an hour in this general direction...')
+ Question of embedding paths, i.e., locking in more damage to some parts of the landscape vs others

## Conclusions {#sec-conclusions}
To cover:
+ Novelty of fitting land cover specific hiking functions
+ A method for exploring potential impacts in a novel environment
+ A method for proposing less damaging plans for expeditions
+ Other?

>>>>

## Discussion {#sec-discussion}
To cover:

+ Figure of the largest study site?
+ Limitations of the method:
  + Data concerns, esp. opportunistic nature of the GPS data
  + Would higher resolution network be useful?
  + Possible limitations of a regularly spaced lattice: extend to a lattice based on e.g., TIN?
  + Reliance of shortest paths as a guide to behaviour
  + Some minor issues regarding the difference between directed and undirected graphs
+ Relevance of radius limits on betweenness: the implicit model of movement in this approach (short horizons, no existing paths, 'keep going for half an hour in this general direction...')
+ Question of embedding paths, i.e., locking in more damage to some parts of the landscape vs others

## Conclusions {#sec-conclusions}
To cover:

+ Novelty of fitting land cover specific hiking functions
+ A method for exploring potential impacts in a novel environment
+ A method for proposing less damaging plans for expeditions
+ Other?
